They're Clutching up! Team Momentum in Round-Based Esports

### 2022-08-17 paper/paper.tex
reduce long eq 3

\begin{equation}\protect\hypertarget{eq:pwkr}{}{
  \hat{P}^{kr,\text{win}}_{E,\text{unadj.}} = \hat{P}(\text{win round | k-round winning streak, series lasting r rounds})=\{
    \begin{array}{cl}
    \frac{6 - k}{i - k}, & \text{team wins series} \\
    \frac{11 - 6 - k}{i - k}, & \text{team loses series}
    \end{array}.
  }\label{eq:pwkr}
\end{equation}

\(\hat{P}^{kr,loss}_{E,\text{unadj.}} = \hat{P}(\text{lose round | k-round losing streak, series lasting r rounds})\)
can be formulated symmetrically.

@@

\begin{longtable}{rrrrrrr}
\caption{First, observed proportion of wins ($\hat{P}^{kr,\text{win}}_O$) and expected proportion of wins, both un-adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$), after 3-round win streak, for a series lasting $r$ rounds. Second, observed proportion of losses ($\hat{P}^{kr,\text{loss}}_O$) and expected proportion of losses, both un-adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$), after 3-round loss streak}\label{tbl:cod-round-win-prop-after-k-wins} \\
\toprule
\multicolumn{7}{c}{\text{3 round win streak}} \\
 &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 
\cmidrule(lr){4-5} \cmidrule(lr){6-7}
$r$ & $N^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$ &  $p$-value & $\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$ & $p$-value \\ 
\midrule
7 & 209 & $75\%$ & $75\%$ & 0.58 & $61\%$ & <=0.01 \\ 
8 & 209 & $62\%$ & $60\%$ & 0.28 & $45\%$ & <=0.01 \\ 
9 & 193 & $52\%$ & $50\%$ & 0.33 & $35\%$ & <=0.01 \\ 
10 & 151 & $44\%$ & $43\%$ & 0.45 & $29\%$ & <=0.01 \\ 
11 & 150 & $40\%$ & $38\%$ & 0.29 & $25\%$ & <=0.01 \\ 
\toprule
\multicolumn{7}{c}{\text{3 round loss streak}} \\
 &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 
\cmidrule(lr){4-5} \cmidrule(lr){6-7}
$r$ & $N^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$ &  $p$-value & $\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$ & $p$-value \\ 
\midrule
10 & 60 & $13\%$ & $14\%$ & 0.64 & $10\%$ & 0.26 \\ 
11 & 129 & $24\%$ & $25\%$ & 0.63 & $16\%$ & <=0.01 \\ 
\bottomrule
\end{longtable}

>>>>

\begin{equation}\protect\hypertarget{eq:pwkr}{}{
  \hat{P}^{kr,\text{win}}_{E,\text{unadj.}} = \hat{P}_{E,\text{unadj.}}(\text{win | k, r})=\{
    \begin{array}{cl}
    \frac{6 - k}{i - k}, & \text{team wins series} \\
    \frac{11 - 6 - k}{i - k}, & \text{team loses series}
    \end{array}.
  }\label{eq:pwkr}
\end{equation}

\(\hat{P}^{kr,loss}_{E,\text{unadj.}}\) can be formulated symmetrically.

@@

\begin{tabbing}
\begin{longtable}{rrrrrrr}
\caption{First, observed proportion of wins ($\hat{P}^{kr,\text{win}}_O$) and expected proportion of wins, both un-adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$), after 3-round win streak, for a series lasting $r$ rounds. Second, observed proportion of losses ($\hat{P}^{kr,\text{loss}}_O$) and expected proportion of losses, both un-adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$), after 3-round loss streak}\label{tbl:cod-round-win-prop-after-k-wins} \\
\toprule
\multicolumn{7}{c}{\text{3 round win streak}} \\
 &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 
\cmidrule(lr){4-5} \cmidrule(lr){6-7}
$r$ & $N^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$ &  $p$-value & $\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$ & $p$-value \\ 
\midrule
7 & 209 & $75\%$ & $75\%$ & 0.58 & $61\%$ & <=0.01 \\ 
8 & 209 & $62\%$ & $60\%$ & 0.28 & $45\%$ & <=0.01 \\ 
9 & 193 & $52\%$ & $50\%$ & 0.33 & $35\%$ & <=0.01 \\ 
10 & 151 & $44\%$ & $43\%$ & 0.45 & $29\%$ & <=0.01 \\ 
11 & 150 & $40\%$ & $38\%$ & 0.29 & $25\%$ & <=0.01 \\ 
\toprule
\multicolumn{7}{c}{\text{3 round loss streak}} \\
 &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 
\cmidrule(lr){4-5} \cmidrule(lr){6-7}
$r$ & $N^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$ &  $p$-value & $\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$ & $p$-value \\ 
\midrule
10 & 60 & $13\%$ & $14\%$ & 0.64 & $10\%$ & 0.26 \\ 
11 & 129 & $24\%$ & $25\%$ & 0.63 & $16\%$ & <=0.01 \\ 
\bottomrule
\end{longtable}
\end{tabbing}
